---
title: "data analysis script"
author: "mel"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    fig_width: 10
    fig_height: 6

---
research question: Depending on whether stigma (cmoderator) will influence the relationship between pss and emotional 
stigma: categorical
pss/ emotional: continous

linear model

looking at the relationship between valence, condition(nonstigma/stigma), and percieved stress

condition 1: non stigamtized, 2= stigmatized

valence (negative emotion)1-9(postive emotions)
pss: (not stressed)1-5(very stressed)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
library(knitr)
library(ggplot2)
library(showtext)
library(devtools)

```
## Load Data
```{r load}
data <- read.csv("STGREW1b_comb.csv")

```
## Background
research question
what is the study design 
what are the predictor variables 
what are the outcome variables 
what roughly happened in the study 
What are your predictions/ excpeted





## Reverse Code Perveived Stress 
```{r recode}
#recode 2 varibles Pss: Q2_2, Q2_3
data <- data %>% 
  mutate_at(vars(Q2_2, Q2_3), function(x){6-x})
```
## Average and Create A Column for Percieved Stress
```{r pss col}
# make one col of pss/ average rows four items t create one single pss col
data <- data %>% 
  rowwise() %>% 
  mutate(PSS = mean(c_across(starts_with('Q2_')), na.rm = TRUE))

```
## Format Condition to Catergorical
```{r condition col}
# condition col / get condition varibale in right format / need to be in factors (categorical)
data$Condition <- factor(data$Condition,
                          levels=c(1,2),
                          labels=c("Control","Stigma"))
data$Condition <- as.factor(data$Condition)
```
## Descriptives of Condition
```{r desc condition}

```
## Descriptives of Emotional Valence 
```{r desc emotional valence}

```
## Descriptives of Percieved Stress
```{r desc percieved stress}

```
## Create a Linear Regression Model
```{r linear model}
# lm formula
model <- lm(mat_valence ~  Condition * PSS, data)

#see what output is
 summary (model)

```
## Create Linear Regression Model Graph 
```{r ggplot}

theme_name = "theme_barbie" # Pick which theme you want

theme_url = paste0("https://raw.githubusercontent.com/MatthewBJane/theme_park/main/", theme_name ,".R")
source_url(theme_url)

plot <- ggplot(data, aes(x= PSS, y=mat_valence, color=Condition)) +
  geom_point() +
  geom_smooth(method = "lm", se = T, alpha = .2) +
  labs(x="Perceived Stress", y="Emotional Valence") +
  theme_barbie(barbie_font = TRUE) +
  scale_color_manual(values=c(light_color_barbie,dark_color_barbie)) 
  
  


plot
  

  

```
## Conclusion 
Restate predictions
What are the results
were the results supported/ sig?