---
title: "Examining relationships among stigmatization, stress and emotions"
author: "mel"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    fig_width: 10
    fig_height: 6

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(stringr)
library(knitr)
library(ggplot2)
library(showtext)
library(devtools)
library(ThemePark)
```
# Background

## Research Question
Does perceived stress function as a moderator in the relationship between stigma and emotional valence (positive or negative affect) experienced by individuals?

## Study Design

Between-Subject Design

**Predictors:** 

1. Perceived Stress: 1(not stressed)-5(very stressed)
  + Outcome Variable
  + Continuous

2. Condition: 1:non-stigmatized, 2= stigmatized
  + Predictor Variable
  + Categorical

**Outcome:**  
1. Emotional Valence: 1(negative)-9(positive)
  + Outcome Variable
  + Continuous
  
  
## Predicted Results
The interaction between perceived stress on stigma and emotional valence is expected to be significant. Participants facing high perceived stress are predicted to have high stigma and low emotional valence (most negative affect) compared to other group. 

# Data Preperation

## Load Data
```{r load}
data <- read.csv("STGREW1b_comb.csv")
```

## Reverse Code Perveived Stress 
```{r recode}
#recode 2 varibles Pss: Q2_2, Q2_3
data <- data %>% 
  mutate_at(vars(Q2_2, Q2_3), function(x){6-x})
```
## Average and Create A Column for Percieved Stress
```{r pss col}
# make one col of pss/ average rows four items t create one single pss col
data <- data %>% 
  rowwise() %>% 
  mutate(PSS = mean(c_across(starts_with('Q2_')), na.rm = TRUE))

```
## Format Condition to Catergorical
```{r condition col}
# condition col / get condition varibale in right format / need to be in factors (categorical)
data$Condition <- factor(data$Condition,
                          levels=c(1,2),
                          labels=c("Control","Stigma"))
data$Condition <- as.factor(data$Condition)
```

# Data Analysis


## Descriptives



### Descriptives of Condition

```{r}
sum(data$Condition == "Control")
sum(data$Condition == "Stigma")
```
### Descriptives of Emotional Valence 
```{r desc emotional valence}
c(summary(data$mat_valence),"SD"=sd(data$mat_valence,na.rm=T))
```
### Descriptives of Percieved Stress
```{r desc percieved stress}
c(summary(data$PSS),"SD"=sd(data$PSS,na.rm=T))
```

## Linear Regression Model
The interaction between perceived stress on stigma and emotional valence was not significant. This finding was not aligned with our hypothesis. This result could be due to an inadequate sample size or it could be that there is no relationship between stigma and stress.

### Create a Linear Regression Model
```{r linear model}
# lm formula
model <- lm(mat_valence ~  Condition * PSS, data)

#see what output is
 summary (model)

```
### Create Linear Regression Model Graph 


```{r ggplot}


plot <- ggplot(data, aes(x= PSS, y=mat_valence, color=Condition)) +
  geom_point() +
  geom_smooth(method = "lm", se = T, alpha = .2) +
  labs(x="Perceived Stress", y="Emotional Valence") +
  theme_barbie(barbie_font = TRUE) +
  scale_color_manual(values=c("lightpink","hotpink3")) 
  

plot
```

 